\singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant floral and reproductive traits determine interactions with floral visitors}

### 2021-08-23 Supplementary_Material/Supplementary_Material.Rmd
Figure of flower morphologies added to supplementary text

Description of the traits compiled in this study

@@

-	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape. We divided the flowers in 8 main different categories: open, tube, campanulate, funnelform, papilionaceous, spike and capitulum.

@@

>>>>

Description of the traits compiled in this study with an illustrative figure of the main flower morphologies (Supplementary text Fig 1)

@@

@@

-	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape. We divided the flowers in 8 main different categories: open, bowl, tube, campanulate, funnelform, papilionaceous, brush and capitulum. However, we ended up groupping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary text Fig. 1).

```{r pressure, echo=FALSE, fig.cap="", out.width = '65%',fig.align='center', fig.cap="\\textbf{Supplementary text Fig. 1 | Main floral morphologies considered in this study.} All species were groupped within these categories for analysis: tube (a), papilonaceous (b), open (c), capitulum (d), campanulate (e) and brush (f)."}
knitr::include_graphics("../Images/flower_shapes.png")
```
